---
title: "R Notebook"
output: word_documnet
---

# Question 2.8

1. Let X~N(5,4^2). Compute P(-7<X<7)
```{r}
prob_norm_x<-pnorm(7,5,4)-pnorm(-7,5,4);prob_norm_x
```
2.Generate a random sample of size n=100 from standard normal distribution. Calculate its mean, median and standar deviation(make use of the function set.seed).
```{r}
set.seed(seed=123)
norm_x<-rnorm(100)
mean_x<-mean(norm_x);mean_x
median_x<-median(norm_x);median_x
stdDev_x<-sd(norm_x);stdDev_x
```

3. Obtain upper 5% and lower 2.5% point of a standard normal distribution.
Memorize it(1.645 and -1.96 thses are Z-scores).
```{r}
upp_x<-qnorm(.025);upp_x
low_x<-qnorm(.05,lower.tail = F);low_x
```

4. Report the density function f(x) for x=20 where X~N(20,5^2)
```{r}
den_x<-dnorm(20,mean = 20,sd=5);den_x
```
# Data Storage
#### Data Frame data[unit no,variable no]
```{r}
library(MASS)
attach(Boston)
class(Boston)
View(Boston)
str(Boston)
head(Boston)
names(Boston)
attributes(Boston)
Boston$crim #Extract crim
summary(Boston)


mydata<-edit(Boston)
save(mydata,file = "mydata.RData")
getwd()
load("mydata.RData")
View(mydata)
a<-1:5
b<-6:10
c<-data.frame(a,b);c
```

# Question 3.1


```{r}
mathematics<-c(87,65,32,99,47,65,76,81,55,69,85,90,49,76,21)
statistics<-c(92,87,55,84,90,95,47,79,83,84,65,60,81,99,50)
Gender<-c('M','M','F','F','M','M','M','F','M','F','F','M','F','M','F')
df<-data.frame(mathematics,statistics,Gender)
View(df)
str(df)
attributes(df)
```
1.
```{r}
df[2]
```
2.
```{r}
df$mathematics[3]
```
3.
```{r}
df[3,]
```
4.
```{r}
df[df$statistics>75,]
```
5.
```{r}
df[df$mathematics>70 | df$statistics>80,]
```

6.
```{r}
df[df$Gender!='F',]
```
7.
```{r}
df[df$statistics>65,'mathematics']
df$mathematics[df$statistics>65]
```
8.
```{r}
mean(df$mathematics)
```
9.
```{r}
summary(df)
```
10.
```{r}

```
11.
```{r}
sd(df$statistics)
```
```{r}
sapply(df,sd)
```


```{r}
sapply(df,mean)
#also another way
# colMeans(df[,-3])
```
11.
```{r}
sd(df$statistics)
```

```{r}
mean_maths<-mean(df[,1])
sd_maths<-sd(df[,1])
tr_maths<-(df[,1]-mean_maths)/sd_maths;tr_maths
sta_maths<-scale(df$mathematics);sta_maths
# mean is zero and variance 1 as its a standard normal 
```

```{r}
head(df,3)
```
```{r}
library(summarytools)
freq(df$Gender)
table(df[,3])
```
Make a scatterlpot of marks in mathematics and statistics.pass a fitted line through the scatter of the points.
```{r}
plot(df$mathematics,df$statistics,type = "p",
     xlab = "mathematics",
     ylab = "statistics",
     main = "Scatterplot between Mathematics nad Statistics",
     col=c(rep("blue",length(df$mathematics)),
           rep("red",length(df$statistics))))
lm(mathematics~statistics)
```
